Thread Pool Implementation in C

### 2018-05-03 thread-pool-implementation/paper.tex
add one pic

We create same tasks for every implementation to execute to ensure fairness. we've tested(need some work here)...

@@

	% This is how you define a table: the [!hbt] means that LaTeX is forced (by the !) to place the table exactly here (by h), or if that doesnt work because of a pagebreak or so, it tries to place the table to the bottom of the page (by b) or the top (by t).
	%\begin{table}[!hbt]
		% Center the table
	%\begin{center}
	%	\caption{Simulation Parameters}
	%	\label{tab:simParameters}
		% Table itself: here we have two columns which are centered and have lines to the left, right and in the middle: |c|c|
	%	\begin{tabular}{|c|c|}
	%		% To create a horizontal line, type \hline
	%		\hline
	%		% To end a column type &
	%		% For a linebreak type \\
	%		Information message length & $k=16000$ bit \\
	%		\hline
	%		Radio segment size & $b=160$ bit \\
	%		\hline
	%		Rate of component codes & $R_{cc}=1/3$\\
	%		\hline
	%		Polynomial of component encoders & $[1 , 33/37 , 25/37]_8$\\
	%		\hline
	%	\end{tabular}
	%	\end{center}
	%\end{table}

>>>>

We create same tasks for every implementation to execute to ensure fairness. we've selected three types of tests that represent three typical scenarios in most applications. We designed a task that accesses file system and performs read and write operations. Since accessing file system usually requires blocking which generates large overhead, this task is perfect to represent tasks that takes more than a few CPU cycles to finish. We also designed a task that task an argument, and then computer then sum based on the input and generates a simple hash value. This represents a short to medium tasks present in most applications and we selected it as a candidate to represent short tasks. We also include a task that does nothing in order to test sheer performance of the thread pool without the influence of any outside factors. In addition, we mixed the number of long and shorts tasks in each benchmark in order to generalize the real life scenario where a mixture of different tasks are executed. We want to show that the speedup is not or at least minimally affected by the type of tasks executed.\\

\begin{figure}[!hbt]
		% Center the figure.
		\begin{center}
		% Include the eps file, scale it such that it's width equals the column width. You can also put width=8cm for example...
		\includegraphics[width=\columnwidth]{test_1.png}
		% Create a subtitle for the figure.
		\caption{Benchmark speedup using long blocking tasks and short tasks. From left to right each section represents: long 25\% with short 75\%, long 50\% with short 50\%, and long 75\% with short 25\%. Green bar: pthread per task. Blue: Thread pool. Yellow: pthread per core. Dark Green: Goroutines}
		% Define the label of the figure. It's good to use 'fig:title', so you know that the label belongs to a figure.
		\label{fig:tf_plot}
		\end{center}
	\end{figure}

@@
